---
title: "Amazon Product Analysis"
authors: 'Nathan Thomas, Benjamin Tuohey, Ivan Voinov'
output: html_notebook
---

# Importing/Cleaning Data
```{r}
Amazon_Products <- read.csv('Amazon_Product.csv')
head(Amazon_Products)
```

## Cleaning Data
```{r}
colnames(Amazon_Products)
```

### Removes 800+ empty columns - filters down to 14
```{r}
Amazon_Products_Cleaned <- subset(Amazon_Products, select = c(uniq_id, product_name, manufacturer, price, number_available_in_stock, number_of_reviews, number_of_answered_questions, average_review_rating, amazon_category_and_sub_category, description, product_information, product_description, items_customers_buy_after_viewing_this_item, customer_questions_and_answers))
```

```{r}
head(Amazon_Products_Cleaned)
```

### Writes Dataset as CSV for export
```{r}
write.csv(Amazon_Products_Cleaned,'Amazon_Products_Cleaned.csv')
```

### Convert Price from Pound to Dollar and variable transformation

Price is currently character, need to remove the pound symbol and convert to float type
```{r}
Amazon_Products_Cleaned$price<-gsub("£","",as.character(Amazon_Products_Cleaned$price))
```

```{r}
library(tidyverse)
Amazon_Products_Cleaned <- Amazon_Products_Cleaned %>%
  mutate(price = as.numeric(price), 
         number_of_reviews = as.numeric(number_of_reviews),
         number_of_answered_questions = as.numeric(number_of_answered_questions))
Amazon_Products_Cleaned$price <- Amazon_Products_Cleaned$price*1.30
```

### Convert review rating to number

```{r}
Amazon_Products_Cleaned$average_review_rating <- substr(Amazon_Products_Cleaned$average_review_rating,1,3)
Amazon_Products_Cleaned <- Amazon_Products_Cleaned %>%
  mutate(average_review_rating = as.numeric(average_review_rating))
  
```


# Initial Statistics/Plots
## Statistics

```{r}
Amazon_Products_Cleaned %>%
  summarise(num_cases = n(), 
            mean_price = mean(price, na.rm=T),
            med_price = median(price, na.rm=T),
            mean_reviews = mean(number_of_reviews, na.rm=T),
            mean_rating = mean(average_review_rating, na.rm=T)
            )
```

```{r}
Amazon_Products_Cleaned %>% 
  group_by(manufacturer) %>%
  summarise(num_prod = n()) %>%
  arrange(desc(num_prod))
```



## Plots
###Boxplot
```{r}
Amazon_Products_Cleaned %>%
  ggplot(aes(y=price)) +
  geom_boxplot()
```
There are a lot of outliers, let's adjust the scale.

```{r}
Amazon_Products_Cleaned %>%
  ggplot(aes(y=price)) +
  geom_boxplot() +
  ylim(0,50)

```





# Clustering
### Looking for groups

```{r}
# pairs can only look at numeric variables
Amazon_Products_Cleaned_numeric <- Amazon_Products_Cleaned %>%
  select(price, number_of_reviews, number_of_answered_questions, average_review_rating)
pairs(Amazon_Products_Cleaned_numeric)
```



# Linear Regression
## Validation setup
```{r}

set.seed(380)
Amazon_Products_Cleaned_numeric <- Amazon_Products_Cleaned_numeric %>%
  filter(is.na(price) == F)

train_obs <- createDataPartition(Amazon_Products_Cleaned_numeric$price, , p = 0.5, list = FALSE)

# generating training dataset from the train_obs
training_df <- Amazon_Products_Cleaned_numeric[train_obs, ]
training_df

testing_df  <- Amazon_Products_Cleaned_numeric[-train_obs, ]
testing_df
```


## Feature Selection

```{r}
library(leaps)
regfit_full = regsubsets(price ~ ., data = training_df,  nvmax = 4, method="exhaustive")
summary(regfit_full)
```

```{r}
reg_summary <- summary(regfit_full) #get the summary

par(mfrow=c(2,2))
#rss plot -  NOT USEFUL
plot(reg_summary$rss ,xlab="Number of Variables ",ylab="RSS",type="l")

#adjr2 plot
plot(reg_summary$adjr2 ,xlab="Number of Variables ", ylab="Adjusted RSq",type="l")
max_adjr2 <- which.max(reg_summary$adjr2)
points(max_adjr2,reg_summary$adjr2[max_adjr2], col="red",cex=2,pch=20)

# AIC criterion (Cp) to minimize
plot(reg_summary$cp ,xlab="Number of Variables ",ylab="Cp", type='l')
min_cp <- which.min(reg_summary$cp )
points(min_cp, reg_summary$cp[min_cp],col="red",cex=2,pch=20)

# BIC criterion to minimize
plot(reg_summary$bic ,xlab="Number of Variables ",ylab="BIC",type='l')
min_bic <- which.min(reg_summary$bic)
points(min_bic,reg_summary$bic[min_bic],col="red",cex=2,pch=20)
```

## Model Analysis
```{r}
model_full <- lm(price ~ 0+., data = training_df)
summary(model_full)
```

```{r}
simp_model <- lm(price~0+average_review_rating, data = training_df)
summary(simp_model)
```


## Cross-validation

```{r}
predictions <- predict(model_full, testing_df)
```

```{r}
data.frame( R2 = R2(predictions, testing_df$price, na.rm=T),
            RMSE = RMSE(predictions, testing_df$price, na.rm=T),
            MSE = RMSE(predictions, testing_df$price, na.rm=T)^2,
            MAE = MAE(predictions, testing_df$price, na.rm=T))
```

```{r}
model1 <- lm(data = training_df, price ~ poly(average_review_rating,2))
summary(model1)

# power 3
model2 <- lm(data = training_df, price ~ poly(average_review_rating,3))
summary(model2)
```

```{r}
predictions1 <- predict(model1, testing_df)

predictions2 <- predict(model2, testing_df)
```

```{r}
rbind(data.frame( R2 = R2(predictions, testing_df$price, na.rm=T),
            RMSE = RMSE(predictions, testing_df$price, na.rm=T),
            MSE = RMSE(predictions, testing_df$price, na.rm=T)^2,
            MAE = MAE(predictions, testing_df$price, na.rm=T)),
data.frame( R2 = R2(predictions, testing_df$price, na.rm=T),
            RMSE = RMSE(predictions, testing_df$price, na.rm=T),
            MSE = RMSE(predictions, testing_df$price, na.rm=T)^2,
            MAE = MAE(predictions, testing_df$price, na.rm=T)))
```


## Assumption Checking










